FraCaS: 80 percent complete

### 2019-02-28 paper2018/paper.tex
some more compression and fixes

\paragraph{Adjectives}
In our system, we interpret gradable adjectives using a pair of a
measure $m : objects → Z$ and and a threshold $τ : Z$, where $Z$ is
treated as an abstract ordered ring by Coq. (This structure has no
dynamic aspect in our model, and thus is entirely handled within Coq.)
For subsective adjectives, $τ$ will additionally depend on the class
of the object in question. This structure has the benefit that
opposite adjectives can be easily represented (measures are opposites
$∀x. m_1 x = -m_2 x$ and thresholds do not overlap $τ_1 + τ_2 >
0$). Formalization aside, this idea is reminiscent of degree-based
approaches to gradable adjectives of
\citet{Cresswell:1976,Kennedy:2007}.  Additionally,
adjectival phrases, as present in the FraCaS suite, are interpreted as
linear inequations in $Z$. Solving systems of such inequations is
decidable.
% SC
%Indeed, the tactic that Coq offers for this purpose can
%solve all such problems in the FraCaS suite, automatically.

@@

We evaluated FraCoq against 8 sections of the FraCaS test suite, for a
total of 259 cases. We excluded only section 7, ``temporal reference''. The reason for
doing so is that, in our view, it contains too many examples which
require \textit{ad-hoc} treatment, and thus makes little sense to
include without complementing it with a more thorough suite which
captures a more complete landscape of the phenomena that section 7
touches.

FraCaS intends to classify each problem as either entailment (YES),
entailment of the opposite (NO) or no entailment (UNK).  In this work,
we have amended the FraCaS suite to correct a few problems. First,
certain test case are not formed correctly. Those were already
identified by Bill MacCartney \citet{maccartney:2007} as such (using an ``undef''
labelling), and we removed those. Second, a few test cases occur twice
in the suite, but with two different labelling (one YES and one UNK),
with an annotation that those labellings correspond to different
readings. However, elsewhere in the suite, if a problem has several
readings but only one has entailment, it occurs only once and is
marked as YES. To make the test suite consistent, if one reading
yields entailment we have always considered it as YES. We have also
removed case 199 (which appears to be vacuous). Finally we changed the
labelling of 6 cases
%(SC: Shall we remove this to the supplementary material and just say to have a look at how we amended the suite?)
% the cases listed in Table \ref{tab:overrulings},
which appeared to have been
misclassified (as justified in supplementary material). We note that the majority of the mistaken
classifications occur in sections 3 and 4, which have not been
previously attempted and thus, we propose, have not been properly
scrutinized.
% \begin{table}
%   \centering
%   \small
% \begin{tabularx}{\columnwidth}{ccp{3.8cm}}
%  test case & new class & comment \\ \hline
%     005 & UNK & missing hypothesis: there are italian tenors \\
%    056 &  Yes & Already identified as such by MacCartney \\
%   069 & Unk & Mary could have used someone else's workstation \\
%   119 & Unk & \textit{ibid.} \\
%   181 & Yes & for the same reason as 180 \\
%   226 & Yes &
% \end{tabularx}
%   \caption{Overruled FraCaS cases}
%   \label{tab:overrulings}
% \end{table}

>>>>

\paragraph{Adjectives}
In our system, we interpret gradable adjectives using a pair of a
measure $m : objects → Z$ and a threshold $τ : Z$, where $Z$ is
treated as an abstract ordered ring by Coq. (This structure has no
dynamic aspect in our model, and thus is entirely handled within Coq.)
For subsective adjectives, $τ$ will additionally depend on the class
of the object in question. This structure has the benefit that
opposite adjectives can be easily represented (measures are opposites
$∀x. m_1 x = -m_2 x$ and thresholds do not overlap $τ_1 + τ_2 >
0$). Formalization aside, this idea is reminiscent of degree-based
approaches to gradable adjectives of
\citet{Cresswell:1976,Kennedy:2007}.  Additionally
adjectival predicates, as present in the FraCaS suite, are interpreted as
linear inequations in $Z$. Solving systems of such inequations is
decidable.
% SC
%Indeed, the tactic that Coq offers for this purpose can
%solve all such problems in the FraCaS suite, automatically.

@@

We evaluated FraCoq against 8 sections of the FraCaS test suite, for a
total of 259 cases. We excluded only section 7, ``temporal reference''.
% The reason for
% doing so is that, in our view, it contains too many examples which
% require \textit{ad-hoc} treatment, and thus makes little sense to
% include without complementing it with a more thorough suite which
% captures a more complete landscape of the phenomena that section 7
% touches.

FraCaS classifies each problem as either entailment (YES),
entailment of the opposite (NO) or no entailment (UNK).  In this work,
we have amended the FraCaS suite to correct a few problems. First,
certain test case are not formed correctly. Those were already
identified by \citet{maccartney:2007} as such (using an ``undef''
labelling), and we removed those. Second, a few test cases occur twice
in the suite, but with two different labellings (one YES and one UNK),
with an annotation that those labellings correspond to different
readings. However, elsewhere in the suite, if a problem has several
readings but only one has entailment, it occurs only once and is
marked as YES. To make the test suite consistent, if one reading
yields entailment we have always considered it as YES. We have also
removed case 199 (which appears to be vacuous). Finally we changed the
labelling of 6 cases
%(SC: Shall we remove this to the supplementary material and just say to have a look at how we amended the suite?)
% the cases listed in Table \ref{tab:overrulings},
which appeared to have been
misclassified (as justified in supplementary material). We note that the majority of the mistaken
classifications occur in sections 3 and 4, which have not been
previously attempted and thus, we propose, have not been properly
scrutinized.
% \begin{table}
%   \centering
%   \small
% \begin{tabularx}{\columnwidth}{ccp{3.8cm}}
%  test case & new class & comment \\ \hline
%     005 & UNK & missing hypothesis: there are italian tenors \\
%    056 &  Yes & Already identified as such by MacCartney \\
%   069 & Unk & Mary could have used someone else's workstation \\
%   119 & Unk & \textit{ibid.} \\
%   181 & Yes & for the same reason as 180 \\
%   226 & Yes &
% \end{tabularx}
%   \caption{Overruled FraCaS cases}
%   \label{tab:overrulings}
% \end{table}
